---
title: "Bitcoin Closed Stock Prices Vs. Covid-19 Effects"
author: "Alston Rice"
date: "2024-01-22"
output: html_document
---


#
# readCovidRDS.R


```{r}
library(tidyverse)
library(lubridate)
max(data$date)
countries <- as.data.frame(table(data$Country_Region))

countries <- as.data.frame(table(data$Country_Region))
countries$pct <- round(100 * countries$Freq / sum(countries$Freq), digits = 4) 

# read bitcoin data 
#source("./R/readBitcoinPrices.R")

subsetCovidData <- data %>%
     filter(date > mdy("01/01/2020") & date < mdy("09/01/2023")) %>%
     rename(Date = date) %>%
     # use base R ifelse() to avoid typing problem with if_else() 
     mutate(Confirmed = ifelse(is.na(Confirmed),0,Confirmed),
            Active = ifelse(is.na(Active),0,Active),
            Deaths = ifelse(is.na(Deaths),0,Deaths),
            Incident_Rate = ifelse(is.na(Incident_Rate),0,Incident_Rate),
            Recovered = ifelse(is.na(Recovered),0,Recovered),
            Country_Region = case_when(Country_Region == "Mainland China" ~ "China",
                                       TRUE ~ Country_Region)) %>%
     # code to summarise() up to one row per country per day
     group_by(Country_Region,Date) %>% 
     summarise(Fatality_Rate = sum(Deaths) / sum(Confirmed) * 100,
               Confirmed = sum(Confirmed),
               Deaths = sum(Deaths),
               Incident_Rate = sum(Incident_Rate)) %>% 
     full_join(.,btcData) %>% filter(!is.na(Confirmed))

#saveRDS(subsetCovidData,"./rdsData/covidAndBitcoinAllCountries.rds")
```

# 19 Variables in the dataset below

```{r}
subsetCovidData %>%
  #filter(Country_Region) %>%
  group_by(Country_Region,Date) %>%  
  summarise(Confirmed = sum(Confirmed),
            Incident_Rate = mean(Incident_Rate),
            Deaths = sum(Deaths),
            #### Calculating the rate to start at Jan 1st- May 29. 2020
            ### for the missing rows not calculating 
            Fatality_Ratio = sum(Deaths) / sum(Confirmed * 100)) %>%
  full_join(.,btcData) %>% filter(!is.na(Confirmed)) %>%
  mutate(time = Date - mdy("01/21/2020"),
         month = month(Date),
         year = year(Date),
         week = week(Date),
         dailyConfirmed = if_else(Date == mdy("01/22/2022"),Confirmed,Confirmed - lag(Confirmed)),
         dailyDeaths = if_else(Date == mdy("01/22/2022"),Deaths,Deaths - lag(Deaths)))-> FullCountryTest
```

### Group AVG by Country_Region, Year, Week
##### Group the AVG by WEEK & YEAR.. Countries are NOT used.. Run to see by 
##### training data 2020-2021
#####test data 2022

```{r}
CountryTest1 <- FullCountryTest %>%
  dplyr::group_by(year,week)%>%
  dplyr::summarize(DeathRate = mean(Deaths),
                   ConfirmedRate = mean(Confirmed),
                   CloseRate = mean(Close),
                   Incident_Rate = mean(Incident_Rate)) %>%
  
  ### Ungroup to create W_S as a time series to count the rows  
  ungroup() %>%
  mutate(week_squence = seq(1,n()))


CountryTest2 <- FullCountryTest %>%
  dplyr::group_by(Country_Region, year,week)%>%
  dplyr::summarize(DeathRate = mean(Deaths),
                   ConfirmedRate = mean(Confirmed),
                   CloseRate = mean(Close))%>%
  dplyr::ungroup()

boxplot(DeathRate~year, data=CountryTest1, main= "year rating for the observation in Death Rate",col=c("blue", "green", "red"))
boxplot(CloseRate~year, data=CountryTest1, main= "Year Obvservations in Close Rate Without Country",col=c("blue", "green", "red"))
boxplot(CloseRate~year, data=CountryTest2, main= "Year Obvservations in Close Rate With Country",col=c("blue", "green", "red"))
### Looking over the Regression analysis
##### From original dataset above
LMThree2<-lm(CloseRate~year + DeathRate + ConfirmedRate, data=CountryTest2)
summary(LMThree2)

## From the past dataset with Dr. Gardner
LMThree1<-lm(CloseRate~year + DeathRate + ConfirmedRate, data=CountryTest1)
summary(LMThree1)
```

## Split data between train and test/ Validation
###First 776 rows will be used for training a multiple linear regression 
## training the data from the dates
### which date do I want to stop at?


# Run regression model with all the independent variables in the model


```{r}
####  Run 1 time   ####

## setting the training and test data for time series
trainThree<- CountryTest1[1:82,] ## copy the first 82 rows
str(trainThree)

#last rows to 138
testThree<- CountryTest1[83:138,] #Copy the last rows
```



```{r}
# Run regression model with all the independent variables in the model
#BitTraining33<- lm(CloseRate~ year + DeathRate + Incident_Rate
#               + ConfirmedRate + week(), data=trainThree)
BitTraining33<- lm(CloseRate~., data=trainThree)
summary(BitTraining33)
#Run a stepAIC model
stepBitTrain33<-stepAIC(BitTraining33,direction="both")
## 47% of the variation of the variables
summary(stepBitTrain33)
```

### Linear model

```{r}
#make this example reproducible
set.seed(123)
####### For the FINAL MODEL (Train, and test)
#use 70% of dataset as training set and 30% as test set
sample <- sample(c(TRUE, FALSE), nrow(CountryTest1), replace=TRUE, prob=c(0.7,0.3))
trainS  <- CountryTest1[sample, ]
testS   <- CountryTest1[!sample, ]

library(caret)
  ### want all of the X
X_test<- testS%>%dplyr::select(- CloseRate)
### All the Y
Y_test<- testS%>%dplyr::select( CloseRate)
# Custom Control Parameters
Custom <- trainControl(method ="repeatedcv",
                       number = 10,
                       repeats = 5,
                       verboseIter = T)

#Linear Model
set.seed(1234)
l_m<-train(CloseRate~.,
          trainS,
          method = 'lm',
          trControl = Custom)
summary(l_m)
l_m$results
lm
plot(l_m$finalModel)

```

## Ridge Regression

```{r}
#Ridge Regression
## cross validation. the best for the model in lambda is 1
set.seed(1234)
ridge <- train(CloseRate~.,
               trainS,
               method = 'glmnet',
               tuneGrid = expand.grid(alpha = 0,
                                      lambda = seq(0.001,1,length=5)),
               trControl = Custom)
plot(ridge)
summary(ridge)
ridge
```

### Lasso Regression

```{r}
#Lasso Regression
#lambda = 1 means dont need to use   
set.seed(1234)
lasso <- train(CloseRate~.,
               trainS,
               method = 'glmnet',
               tuneGrid = expand.grid(alpha=1,
                                      lambda = seq(0.0001,1,length=5)),
               trControl = Custom)
plot(lasso)
```
####for showing the difference in the Linear, Ridge, Lasso####



```{r}
parameters <- c(seq(0.1, 2, by =0.1) ,  seq(2, 5, 0.5) , seq(5, 25, 1))

lasso<-train(CloseRate~.,
             trainS,
             method = 'glmnet', 
             tuneGrid = expand.grid(alpha = 1, lambda = parameters) ,
             metric =  "Rsquared"
) 

ridge<-train(CloseRate~.,
             trainS,
             method = 'glmnet', 
             tuneGrid = expand.grid(alpha = 0, lambda = parameters),
             metric =  "Rsquared"
### Dont need             
) 
linear<-train(CloseRate~.,
              trainS, 
              method = 'lm',
              metric =  "Rsquared"
)
### the last parameter is 25
print(paste0('Lasso best parameters: ' , lasso$finalModel$lambdaOpt))
print(paste0('Ridge best parameters: ' , ridge$finalModel$lambdaOpt))

library(tidyverse)
#### compare the 3 to see the best fit
### comparing the models

predictions_lasso <- lasso %>% predict(X_test)
predictions_ridge <- ridge %>% predict(X_test)
predictions_lin <- linear %>% predict(X_test)

data.frame(
  Ridge_R2 = R2(predictions_ridge, Y_test),
  Lasso_R2 = R2(predictions_lasso, Y_test),
  Linear_R2 = R2(predictions_lin, Y_test))
```



```{r}
#install.packages("forecast")
library(fpp2)
library(forecast)
library(tseries)


# Create a time series object ### Original occuring dataset
Time <- ts(CountryTest1$CloseRate, start = c(2020), frequency = 54)

# Plot the time series with axis labels
plot(Time, xlab = "Weeks", ylab = "Bitcoin Closing Rate")


# create a new time series for the next 3 years
future_ts <- ts(rep(NA, 1*54), start = c(2023), frequency = 54)
#plot(future_ts, xlab = "Weeks", ylab = "Bitcoin Closing Rate")

# combine the original time series with the future time series
combined_ts <- c(Time, future_ts)
library(forecast)
library(ggplot2)

### the forcasting limit is unsure do to the possibility of change
# Assuming combined_ts is a time series object
# load required libraries


autoplot(forecast(combined_ts, h = 54*1)) +
  labs(title = "Forecast of Bitcoin Closing Rate for the Next 3 Years",
       x = "Weeks",
       y = "Closing Rate")

plot(combined_ts, xlab = "Weeks", ylab = "Bitcoin Closing Rate")
```













## the alignment of the Countries is incorrect. Need to go back and fix

```{r}
final.model<- data.frame(
  as.data.frame.matrix(coef(l_m$finalModel)),
  as.data.frame.matrix(coef(ridge$finalModel)),
  as.data.frame.matrix(coef(lasso$finalModel))
) %>%
  rename(Linear_coef = X1, Ridge_coef = X1.1, Lasso_coef = X1.2)
```






##This is separating countries all together
```{r}
######Variable analysis for the countries. the country China has the lowest death rate and Idia has the next highest death rate and the US country has the highest death rate
boxplot(Deaths~Country_Region, data=FullCountryTest)

GardWeek2 <- FullCountryTest %>%
  dplyr::group_by(Country_Region, year,week)%>%
  dplyr::summarize(DeathRate = mean(Deaths),
                   ConfirmedRate = mean(Confirmed),
                   CloseRate = mean(Close))%>%
  dplyr::ungroup()
```

```{r}
### Looking over the Regression analysis
LMThree<-lm(CloseRate~Country_Region + DeathRate + ConfirmedRate, data=GardWeek2)
summary(LMThree)

```








## R Markdown


## Including Plots

Death rate for all the countries.

```{r pressure, echo=FALSE}
boxplot(Deaths~Country_Region, data=FullCountry)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
